---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# gasexchangeR

gasexchangeR is the interface for data obtained by the photosynthetic measurement systems by LI-COR (LI6400, LI6400XT, LI6800, ...).
It has two main goals:

* Read easily the gasexchange data into data frames.

* Provide visual summary for checking the status during the measurement.

You can install:

* the latest development version from github with

```R
# install.packages("devtools") # if not installed
devtools::install_github("KeachMurakami/gasexchangeR")
```


## Reading

`gasexchangeR` implements the following verb for reading LI6xxx data:

* `read_licor()`: read `.txt` format data obtained by LI6xxx into data frames.
    * warning messages usually originate from parsing procedure for the file header.

```{r demo_read}
library(gasexchangeR)

sample_single <- "https://raw.githubusercontent.com/KeachMurakami/gasexchangeR/master/R/LI6400.txt"
sample_multi <- c("https://raw.githubusercontent.com/KeachMurakami/gasexchangeR/master/R/LI6400.txt",
                  "https://raw.githubusercontent.com/KeachMurakami/gasexchangeR/master/R/LI6400XT.txt")

# simple read
read_licor(file = sample_single)

# include logs for changes in conditions
read_licor(file = sample_single, info_log = T)

# read multiple files into a data frame
read_licor(file = sample_multi)
```


## Visualizations

`gasexchangeR` implements the following verbs useful for visualizations:

* `li_scat()`: view a relationship between variables
    * `li_scat_light()`:
    * `li_scat_co2()`:
    * `li_scat_h2o()`:
    * `li_scat_temp()`:
* `li_course()`: view time course of a variable
* `li_check()`: view primitive plots to check the environmental stability during the measurement

```{r demo_plot}
li_scat(file = sample_multi, color = "VpdL")
li_course(file = sample_multi, color = "Ci")
```


## Session information

```{r sessioninfo}
devtools::session_info()
```
